---
title: "<b>CoMarker</b> - Colocalisation Analysis Report"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmdformats::downcute
---

```{r setup, results='hide', include=FALSE}
library(plyr)
library(knitr)
library(data.table)
library(ggplot2)
library(ggsignif)
library(plotly)
library(clinUtils)
library(flexdashboard)
library(rlist)
library(rmdformats)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE)
knitr::knit_hooks$set(wrap = function(before, options, envir){
  if (before){
    paste0('<', options$wrap, ' align="center">')
  } else {
    paste0('</', options$wrap, '>')
  }
})

```

# Summary

From the data provided, `r (number_marker*9)+6` plots have been produced, with `r sig_count` significant comparison(s) between `r outcome` groups.
  
Each data point represents the average of all images from each case ID, with a total of `r nCases` cases analysed from a set of `r nSamples` samples, averaging `r round((nSamples/nCases),digits=2)` technical replicates per individual. Please note that this average may not always be an integer due to the removal of flagged samples.  

From the raw images, data is only extracted from clusters of conjoining pixels exceeding the inputted minimum area, therefore regions of marker-positive pixels smaller than the minimum area are not analysed.  

The cell counts included in this report describe the number of nuclei that contain the respective marker within the inputted proximity.

## Statistical Significance

The statistical significance of each plot is annotated such that:\
\* = p\<0.05\
\*\* = p\<0.01\
\*\*\* = p\<0.001\
ns = non-significant  
  
# `r region_of_interest` Plots

`r region_of_interest` was selected as the region of interest in this study and plots for the count and area of `r region_of_interest` have been produced below, comparing `r outcome` groups.

## `r region_of_interest` Count and Area

The `r region_of_interest` count plot illustrates the number of `r region_of_interest`-positive regions in each image, while the `r region_of_interest` area plot presents the total area of these regions.

```{r echo=FALSE,}
plot_list[[1]]
```

```{r echo=FALSE,}
plot_list[[2]]
```

# `r reference_marker` Plots

`r reference_marker` was selected as the reference marker in this study and plots for the count of `r reference_marker`-positive cells have been produced below, both respective and irrespective of the region of interest, comparing `r outcome` groups. Plots for the colocalisation of the reference marker with the other analysed marker(s) can be found in the section of the respective marker.

## `r reference_marker` Cell Counts

```{r echo=FALSE,}
plot_list[[3]]
```

```{r echo=FALSE,}
plot_list[[4]]
```

```{r echo=FALSE,}
plot_list[[5]]
```

## % of `r reference_marker`+ Cells in the ROI

```{r echo=FALSE,}
plot_list[[6]]
```

# `r marker1` Plots

`r marker1` was selected as a colocalisation marker in this study and plots for the count of `r marker1`-positive cells have been produced below, both respective and irrespective of the region of interest, comparing `r outcome` groups.

## `r marker1` Cell Counts

```{r echo=FALSE,}
plot_list[[7]]
```

```{r echo=FALSE,}
plot_list[[8]]
```

```{r echo=FALSE,}
plot_list[[9]]
```

```{r echo=FALSE}
plot_list[[10]]
```

## `r marker1` `r reference_marker` Colocalised Cell Counts

The following plots compare the number of cells positive for both `r marker1` and `r reference_marker` within, outside of, and irrespective of the region of interest (`r region_of_interest`).

```{r echo=FALSE}
plot_list[[11]]
```

```{r echo=FALSE,}
plot_list[[12]]
```

```{r echo=FALSE,}
plot_list[[13]]
```

```{r echo=FALSE,}
plot_list[[14]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[15]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("# ", marker2," Plots"  ))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste(marker2," was selected as a colocalisation marker in this study and plots for the count of ",marker2,"-positive cells have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups."))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("##",marker2," Cell Counts"))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[16]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[17]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[18]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[19]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("##",marker2," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker2," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[20]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[21]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[22]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[23]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[24]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}

### Marker3 ###

knitr::asis_output(paste("# ", marker3," Plots"))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste(marker3," was selected as a colocalisation marker in this study and plots for the count of ",marker3,"-positive cells have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("##",marker3," Cell Counts"))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[25]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[26]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[27]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[28]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("##",marker3," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker3," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[29]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[30]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[31]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[32]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[33]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}

### Marker4 ###

knitr::asis_output(paste("# ", marker4," Plots"))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste(marker4," was selected as a colocalisation marker in this study and plots for the count of ",marker4,"-positive cells have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("##",marker4," Cell Counts"))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[34]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[35]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[36]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[37]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("##",marker4," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker4," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[38]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[39]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[40]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[41]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[42]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}

### Marker5 ###

knitr::asis_output(paste("# ", marker5," Plots"))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste(marker5," was selected as a colocalisation marker in this study and plots for the count of ",marker5,"-positive cells have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("##",marker5," Cell Counts"))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[43]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[44]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[45]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[46]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("##",marker5," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker5," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[47]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[48]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[49]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[50]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[51]]
```

# Data

## Raw Data

```{r, echo=FALSE}
DT::datatable(df,
              escape = F,
              rownames = F, 
              extensions = 'Buttons', 
              options = list(dom = 'Blfrtip', 
                             buttons = list('colvis', 
                                            list(extend = 'copy', exportOptions = list(columns=':visible')),
                                            list(extend = 'csv', exportOptions = list(columns=':visible')),
                                            list(extend = 'excel', exportOptions = list(columns=':visible')))))
```

## Averaged Data

```{r, echo=FALSE}
DT::datatable(cbind(metadata$CaseID,summary2),
              colnames = c('Case ID',colnames(summary2)),
              escape = F,
              rownames = F, 
              extensions = 'Buttons', 
              options = list(dom = 'Blfrtip', 
                             buttons = list('colvis', 
                                            list(extend = 'copy', exportOptions = list(columns=':visible')),
                                            list(extend = 'csv', exportOptions = list(columns=':visible')),
                                            list(extend = 'excel', exportOptions = list(columns=':visible')))))
```

# Flagged Images

Samples were flagged if the count was more than `r outliers_threshold` standard deviations from the mean. A total of `r nFlags` replicate(s) with images exceeding this threshold were identified.

```{r, eval=(remove_outliers == TRUE), echo=FALSE}
knitr::asis_output(paste('Flagged images were removed and excluded from the analysis.'))
```

Below are the identifiers for the flagged images.

```{r, echo=FALSE}
DT::datatable(flags,
              escape = F,
              rownames = F, 
              extensions = 'Buttons', 
              options = list(dom = 'Blfrtip', 
                             buttons = list('colvis', 
                                            list(extend = 'copy', exportOptions = list(columns=':visible')),
                                            list(extend = 'csv', exportOptions = list(columns=':visible')),
                                            list(extend = 'excel', exportOptions = list(columns=':visible')))))
```
