---
title: "<b>CoMarker</b> - Colocalisation Analysis Report"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmdformats::downcute
---

```{r setup, results='hide', include=FALSE}
library(plyr)
library(knitr)
library(data.table)
library(ggplot2)
library(ggsignif)
library(plotly)
library(clinUtils)
library(flexdashboard)
library(rlist)


knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache.lazy = FALSE)
knitr::knit_hooks$set(wrap = function(before, options, envir){
  if (before){
    paste0('<', options$wrap, ' align="center">')
  } else {
    paste0('</', options$wrap, '>')
  }
})

```
# Summary

From the data provided, `r (number_marker*9)+6` plots have been produced, with `r sig_count` significant comparison(s) between `r outcome` groups.  
  
Each data point represents total marker-containing area (number of pixels), averaged across all images from each case ID. From the raw images, data is only extracted from clusters of conjoining pixels exceeding the inputted minimum area, therefore regions of marker-positive pixels smaller than the minimum area are not analysed.  
  
The marker area included in this report describes the total marker-contaioning area of each image provided.
  
# Statistical Significance

The statistical significance of each plot is annotated such that:  
  * = p<0.05  
  ** = p<0.01  
  *** = p<0.001  
  ns = non-significant  
  
In this section are the plots which meet our criteria for statistical significance. If there are no plots in this section there are no significant results in the data.  
  

```{r eval=(signif[[name]] != "'ns' 'ns' 'ns'" && sig_count>0), echo=FALSE}
    print(plot_list[[name]])
```

# `r region_of_interest` Plots  

`r region_of_interest` was selected as the region of interest in this study and plots for the count and area of `r region_of_interest` have been produced below, comparing `r outcome` groups.  

## `r region_of_interest` Count and Area  

The `r region_of_interest` count plot illustrates the number of `r region_of_interest`-positive regions in each image, while the `r region_of_interest` area plot presents the total area of these regions.  

```{r echo=FALSE,}
plot_list[[1]]
```

```{r echo=FALSE,}
plot_list[[2]]
```

# `r reference_marker` Plots  

`r reference_marker` was selected as the reference marker in this study and plots for the area containing `r reference_marker` have been produced below, both respective and irrespective of the region of interest, comparing `r outcome` groups. Plots for the colocalisation of the reference marker with the other analysed marker(s) can be found in the section of the respective marker.

## `r reference_marker` Area

```{r echo=FALSE,}
plot_list[[3]]
```

```{r echo=FALSE,}
plot_list[[4]]
```

```{r echo=FALSE,}
plot_list[[5]]
```

## % of `r reference_marker` in the ROI

```{r echo=FALSE,}
plot_list[[6]]
```

# `r marker1` Plots  

`r marker1` was selected as a colocalisation marker in this study and plots for the area containing `r marker1` have been produced below, both respective and irrespective of the region of interest, comparing `r outcome` groups.  
  
## `r marker1` Area

```{r echo=FALSE,}
plot_list[[7]]
```

```{r echo=FALSE,}
plot_list[[8]]
```

```{r echo=FALSE,}
plot_list[[9]]
```

```{r echo=FALSE}
plot_list[[10]]
```

## `r marker1` `r reference_marker` Colocalised Area  

The following plots compare the area (number of pixels) positive for both `r marker1` and `r reference_marker` within, outside of, and irrespective of the region of interest (`r region_of_interest`).  

```{r echo=FALSE}
plot_list[[11]]
```

```{r echo=FALSE,}
plot_list[[12]]
```

```{r echo=FALSE,}
plot_list[[13]]
```

```{r echo=FALSE,}
plot_list[[14]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[15]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("# ", marker2," Plots"  ))
```
  
```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste(marker2," was selected as a colocalisation marker in this study and plots for the area containing ",marker2," have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups."))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("##",marker2," Area"))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[16]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[17]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[18]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[19]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("##",marker2," ",reference_marker," Colocalised Area"))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("The following plots compare the area (number of pixels) positive for both ",marker2," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[20]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[21]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[22]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[23]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[24]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}

### Marker3 ###

knitr::asis_output(paste("# ", marker3," Plots"))
```
  
```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste(marker3," was selected as a colocalisation marker in this study and plots for the area containing ",marker3," have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups.  "))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("##",marker3," Area"))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[25]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[26]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[27]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[28]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("##",marker3," ",reference_marker," Colocalised Area"))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("The following plots compare the area (number of pixels) positive for both ",marker3," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[29]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[30]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[31]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[32]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[33]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}

### Marker4 ###

knitr::asis_output(paste("# ", marker4," Plots"))
```
  
```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste(marker4," was selected as a colocalisation marker in this study and plots for the area containing ",marker4," have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("##",marker4," Area"))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[34]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[35]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[36]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[37]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("##",marker4," ",reference_marker," Colocalised Area"))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("The following plots compare the area (number of pixels) positive for both ",marker4," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[38]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[39]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[40]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[41]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[42]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}

### Marker5 ###

knitr::asis_output(paste("# ", marker5," Plots"))
```
  
```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste(marker5," was selected as a colocalisation marker in this study and plots for the area containing ",marker5," have been produced below, both respective and irrespective of the region of interest, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("##",marker5," Area"))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[43]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[44]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[45]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[46]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("##",marker5," ",reference_marker," Colocalised Area"))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("The following plots compare the area (number of pixels) positive for both ",marker5," and ",reference_marker, " within, outside of, and irrespective of the region of interest (",region_of_interest,").  "))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[47]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[48]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[49]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[50]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[51]]
```
