---
title: "<b>CoMarker</b> - Colocalisation Analysis Report"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: rmdformats::downcute
---

```{r setup, results='hide', include=FALSE}
library(plyr)
library(knitr)
library(data.table)
library(ggplot2)
library(ggsignif)
library(plotly)
library(clinUtils)
library(flexdashboard)
library(rlist)


knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache.lazy = FALSE)
knitr::knit_hooks$set(wrap = function(before, options, envir){
  if (before){
    paste0('<', options$wrap, ' align="center">')
  } else {
    paste0('</', options$wrap, '>')
  }
})

```
# Summary

From the data provided, `r (number_marker*3)+1` plots have been produced, with `r sig_count` significant comparison(s) between `r outcome` groups.  
  
Each data point represents the average of all images from each case ID, with a total of `r nCases` cases analysed from a set of `r nSamples` samples, averaging `r round((nSamples/nCases),digits=2)` technical replicates per individual. Please note that this average may not always be an integer due to the removal of flagged samples.  

From the raw images, data is only extracted from clusters of conjoining pixels exceeding the inputted minimum area, therefore regions of marker-positive pixels smaller than the minimum area are not analysed.  
  
The cell counts included in this report describe the number of nuclei that contain the respective marker within the inputted proximity.  
  
## Statistical Significance

The statistical significance of each plot is annotated such that:  
  * = p<0.05  
  ** = p<0.01  
  *** = p<0.001  
  ns = non-significant  
  
# `r reference_marker` Plots  

`r reference_marker` was selected as the reference marker in this study and plots for the count of `r reference_marker`-positive cells have been produced below, comparing `r outcome` groups. Plots for the colocalisation of the reference marker with the other analysed marker(s) can be found in the section of the respective marker.

## `r reference_marker` Cell Counts

```{r echo=FALSE,}
plot_list[[1]]
```

# `r marker1` Plots  

`r marker1` was selected as a colocalisation marker in this study and plots for the count of `r marker1`-positive cells have been produced below, comparing `r outcome` groups.  
  
## `r marker1` Cell Counts

```{r echo=FALSE,}
plot_list[[2]]
```

## `r marker1` `r reference_marker` Colocalised Cell Counts  

The following plots compare the number of cells positive for both `r marker1` and `r reference_marker`.  

```{r echo=FALSE}
plot_list[[3]]
```

```{r echo=FALSE,}
plot_list[[4]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("# ", marker2," Plots"  ))
```
  
```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste(marker2," was selected as a colocalisation marker in this study and plots for the count of ",marker2,"-positive cells have been produced below, comparing ",outcome," groups."))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("##",marker2," Cell Counts"))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[5]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("##",marker2," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker2," and ",reference_marker, ".  "))
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[6]]
```

```{r, eval=(number_marker >= 2), echo=FALSE}
plot_list[[7]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}

### Marker3 ###

knitr::asis_output(paste("# ", marker3," Plots"))
```
  
```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste(marker3," was selected as a colocalisation marker in this study and plots for the count of ",marker3,"-positive cells have been produced below, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("##",marker3," Cell Counts"))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[8]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("##",marker3," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker3," and ",reference_marker, ".  "))
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[9]]
```

```{r, eval=(number_marker >= 3), echo=FALSE}
plot_list[[10]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}

### Marker4 ###

knitr::asis_output(paste("# ", marker4," Plots"))
```
  
```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste(marker4," was selected as a colocalisation marker in this study and plots for the count of ",marker4,"-positive cells have been produced below, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("##",marker4," Cell Counts"))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[11]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("##",marker4," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker4," and ",reference_marker, ".  "))
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[12]]
```

```{r, eval=(number_marker >= 4), echo=FALSE}
plot_list[[13]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}

### Marker5 ###

knitr::asis_output(paste("# ", marker5," Plots"))
```
  
```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste(marker5," was selected as a colocalisation marker in this study and plots for the count of ",marker5,"-positive cells have been produced below, comparing ",outcome," groups."  ))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("##",marker5," Cell Counts"))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[14]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("##",marker5," ",reference_marker," Colocalised Cell Counts"))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
knitr::asis_output(paste("The following plots compare the number of cells positive for both ",marker5," and ",reference_marker, ".  "))
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[15]]
```

```{r, eval=(number_marker >= 5), echo=FALSE}
plot_list[[16]]
```

# Data

## Raw Data

```{r, echo=FALSE}
DT::datatable(df,
              escape = F,
              rownames = F, 
              extensions = 'Buttons', 
              options = list(dom = 'Blfrtip', 
                             buttons = list('colvis', 
                                            list(extend = 'copy', exportOptions = list(columns=':visible')),
                                            list(extend = 'csv', exportOptions = list(columns=':visible')),
                                            list(extend = 'excel', exportOptions = list(columns=':visible')))))
```

## Averaged Data

```{r, echo=FALSE}
DT::datatable(cbind(metadata$CaseID,summary2),
              colnames = c('Case ID',colnames(summary2)),
              escape = F,
              rownames = F, 
              extensions = 'Buttons', 
              options = list(dom = 'Blfrtip', 
                             buttons = list('colvis', 
                                            list(extend = 'copy', exportOptions = list(columns=':visible')),
                                            list(extend = 'csv', exportOptions = list(columns=':visible')),
                                            list(extend = 'excel', exportOptions = list(columns=':visible')))))
```